Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-01-31 Multiresolution_framework/ltx/manuscript.tex
minor edits

Typically, a sequence of likelihood values will converge to a stationary point i.e. global (local) maximum or a saddle point. If the sequence of the EM is trapped in a local maximum or a saddle point, a small random perturbation diverges the algorithm from such stationary values \citep{McLachlan1997}. In general, convergence of the EM algorithm to any stationary point depends on the initialisation. In the examples presented in this chapter, a bounded sequence of the state vectors was used to initialise the algorithm, which gave a satisfactory convergence and good state and parameter estimations.

@@

Additional extension for future work include extending the model to capture a $2^{nd}$-order synaptic response kernel, The second order postsynaptic kernel proposed in \citet{VanRotterdam1982} leads to dynamics that are more reminiscent to real postsynaptic potentials.

Another extension of this framework is the inclusion of finite distant-dependant action potential propagation velocity into the parametric neural field equations. In small networks the delays via propagation can be neglected, however they must be accounted for in large scale networks. For instance, it is shown by \citet{Ghosh2008} that inclusion of time delays arising from propagation along connecting fibres are essential for the fluctuations to be appeared in the default networks. Finally, future work should be directed towards applying and validating the framework on real data.

>>>>

Typically, a sequence of likelihood values will converge to a stationary point i.e. global (local) maximum or a saddle point. If the sequence of the EM is trapped in a local maximum or a saddle point, a small random perturbation diverges the algorithm from such stationary values \citep{McLachlan1997}. In general, convergence of the EM algorithm to any stationary point depends on the initialisation. In the examples presented in this paper, a bounded sequence of the state vectors was used to initialise the algorithm, which gave a satisfactory convergence and good state and parameter estimations.

@@

Additional extension for future work include extending the model to capture a second order synaptic response kernel, The second order postsynaptic kernel proposed in \citet{VanRotterdam1982} leads to dynamics that are more reminiscent to real postsynaptic potentials.

Another extension of this framework is the inclusion of finite distant-dependent action potential propagation velocity into the parametric neural field equations. In small networks the delays via propagation can be neglected, however they must be accounted for in large scale networks. For instance, it is shown by \citet{Ghosh2008} that inclusion of time delays arising from propagation along connecting fibres are essential for the fluctuations to be appeared in the default networks. Finally, future work should be directed towards applying and validating the framework on real data.
